A Monte Carlo based new sampling calorimeter toward the measurement of $\gamma$ incident angle

### 2021-07-28 paper.tex
Updates from Overleaf

%The resolution of the reconstruction is defined as the standard deviation of Gaussian function around $\pm$~2 times standard deviations from the peak of the distribution.

@@

\subsection{Parameterization for machine learning setting}
The configuration of the $\XGB$ can be defined with five parameters, described in Tab.~\ref{tab:XgbPar}. The parameters are selected as one providing better angular resolution. It is found that the Max. depth mostly affects the angular resolution, and the resolution is not enhanced for Max. depth~$>$~15 any more. It is also worth mentioning that the N\_estimators larger than 1000 does not provide better resolution with the Max. depth~=~15. The angular resolution with described parameters is found to be about 1.3~degree, as shown in fig.(def).

>>>>

@@

\subsection{Parameterization for machine learning setting}
The configuration of the $\XGB$ can be defined with five parameters, described in Tab.~\ref{tab:XgbPar}. The parameters are selected as one providing better angular resolution. It is found that the Max. depth mostly affects the angular resolution, and the resolution is not enhanced for Max. depth~$>$~15 any more. It is also worth mentioning that the N\_estimators larger than 1000 does not provide better resolution with the Max. depth~=~15. The angular resolution of the reconstruction is defined as the standard deviation of Gaussian function, whose parameters are evaluated by fitting the reconstructed angle distribution. The angular resolution with described parameters is estimated to be about 1.3~degree, as shown in fig.(def).
